Papers

### 2025-06-27 done.qmd
update

@@

2023-05-18 Chaired UKRN/RoRI panel on [The Future of Peer Review](https://www.ukrn.org/event/future-of-peer-review-may2023/). ([Recording](https://youtu.be/BMeSh6esehE), [Slides](https://osf.io/ce3ts/))

>>>>

## 2025

June 16-18th: Panel DPR on DPR at International Conference on the Science of Science and Innovation ([ICSSI](https://icssi.org/)), Copenhagen

June: Stafford, T., Pinfield, S., Butters, A., & Benson Marshall, M. (2025). RoRI Insights: Applicants as reviewers - a Guide to Distributed Peer Review (Version 1). Research on Research Institute. <https://doi.org/10.6084/m9.figshare.29270534.v1>

May - June: Sprint on AI in grantmaking

@@

2023-05-18 Chaired UKRN/RoRI panel on [The Future of Peer Review](https://www.ukrn.org/event/future-of-peer-review-may2023/). ([Recording](https://youtu.be/BMeSh6esehE) and DOI:[10.52843/cassyni.50wy02](https://doi.org/10.52843/cassyni.50wy02), [Slides](https://osf.io/ce3ts/))

### 2025-06-27 papers.qmd
update

@@

-   Vardal, O., Karapanagiotidis, T., Stafford, T., Drachen, A. and Wade, A. (2023) [Unsupervised identification of internal perceptual states influencing psychomotor performance](https://www.biorxiv.org/content/10.1101/2023.09.08.556817v2). bioRxiv 2023.09.08.556817; doi: https://doi.org/10.1101/2023.09.08.556817

@@

-   Zhu, J., Dommett, K., & Stafford, T. (2023). [What makes online political ads unacceptable? Interrogating public attitudes to inform regulatory responses](https://preprints.apsanet.org/engage/apsa/article-details/6462be37f2112b41e99fe9bf). APSA Preprints. doi:10.33774/apsa-2023-rxw1q This content is a preprint and has not been peer-reviewed.

@@

>>>>

- - Boag, R. J., Innes, R. J., Stevenson, N., Bahg, G., Busemeyer, J. R., Cox, G. E., … Forstmann, B. (2024, July 2). [An expert guide to planning experimental tasks for evidence accumulation modelling](https://osf.io/preprints/psyarxiv/snqgp).

@@

@@

@@

-   Zhu, J., Dommett, K., & Stafford, T. (2025). [What makes online political ads unacceptable? Interrogating public attitudes to inform regulatory responses](https://doi.org/10.1057/s41599-025-05114-1 ). Humanities and Social Sciences Communications, 12, 806. https://doi.org/10.1057/s41599-025-05114-1
